\documentclass{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
  %\usepackage{newcent}   % uses new century schoolbook postscript font 
  \setlength{\textheight}{9.5in} % increase text height to fit on 1-page 

  \begin{document} 

  \name{James Clemer\\[12pt]}     % the \\[12pt] adds a blank
  % line after name      

  \address{\bf  PRESENT ADDRESS\\636 Church Street\\Evanston Illinois, 60201\\apt. 901}
  \address{\bf CONTACT \\ (713)540-6960\\https://github.com/jcc333\\clemer19@gmail.com}

  \begin{resume}

  \section{Objective} to leverage the skills I've learned in university and in high-frequency trading in order to solve complex problems.

  \section{Skills}          
  \begin{itemize}
  \item Functional Languages: Racket/PLT Scheme, F$\#$, Haskell, Common LISP, Scala
  \item Object-Oriented Languages: C$\#$, Java, Python, Ruby
  \item Other Languages: go, Prolog, C
  \end{itemize}

  \section{Education}          
  Northwestern University, Evanston Illinois \\
    Bachelor of Arts, Computer Science and Philosophy, June 2014 \\       
    G.P.A. 3.5/4.0          

    \section{Experience}
    \vspace{-0.1in}    
    \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
{\bf Key Coursework:} Programming Languages, Natural Language Processing, Theory of Computation, Philosophy of Math.
\end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
\begin{tabbing}
\hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
{\bf Development Intern} \>IMC Financial Markets \>Summer 2013\\
    \>Chicago, Illinois
    \end{tabbing}\vspace{-20pt}      % suppress blank line after tabbing
    Implemented RESTful components configurations API, gradually integrated into existing system alongside new client driver to persist rapidly-growing data, improving upon performance and extensibility. Implemented full autotrader for a limited portfolio of tech stocks.
    \begin{tabbing}
    \hspace{2.3in}\= \hspace{2.6in}\= \kill % set up two tab positions
{\bf Apprentice Developer} \>GOOD inc               \>Summer 2012\\
    \>Los Angeles, California
    \end{tabbing}\vspace{-20pt}
    Codeveloped media-browsing iOS application for GOOD's recurring "30 Days of GOOD" challenge. Used existing ruby(Rails) framework to develop supporting API, overcoming unstandardized article format.

    \section{Personal Projects}
    \begin{itemize}
    \item {\bf Hopeless} is a Nintendo-hard 3D stealth game.
    \item {\bf Frog Pond:} a programming language designed in NU's TIDAL lab to help children learn basic concepts of programming. The twist is that the code blocks are physical puzzle pieces with embedded microprocessors.
    \item {\bf Lambdas and Logical Forcing:} a thesis which examines the potential for the $\lambda I$ calculus to resolve independent problems in $ZFC$.
    \item {\bf Knut:} an investigation into the efficacy of Recursive Least Squares and Haskell as a guide to speculation on exchange rates.
    \end{itemize}

    \section{Extracarricular Activities}          
    \begin{itemize}
    \item Northwestern Boxing IT Chair
    \item Participant on over 15 student theater production casts and crews
    \item Marathoner
    \item AMC Chapter Vice President
    \item Undergraduate Philosophy Society President
    \item Classical Guitarist with 13 years of experience

    \end{resume}
    \end{document}

